---
title: "Metaanalysis in R"
author: "Alain Kalonji"
date: "`r Sys.Date()`"
format:  
  html:
    theme: lumen
    toc: true
    toc_float: true
    title-block-banner: true
execute:
  echo: false  
---

```{r setup, include=FALSE}
library(meta)
library(metafor)
library(dplyr)
library(readxl)
```
# SCRIPTS
```{r}
metaanalysis_data_1_ <- read_excel("C:/Users/Alain/Downloads/metaanalysis_data (1).xlsx")
df <- metaanalysis_data_1_  
str(df)
```

```{r}
required_cols <- c("N_boys", "Mean_boys_play_male", "SD_boys_play_male",
                  "N_girls", "Mean_girls_play_male", "SD_girls_play_male", "Study")
stopifnot(all(required_cols %in% names(df)))
```

```{r}
m_male_toys <- metacont(
  n.e = df$N_boys,
  mean.e = df$Mean_boys_play_male,
  sd.e = df$SD_boys_play_male,
  n.c = df$N_girls,
  mean.c = df$Mean_girls_play_male,
  sd.c = df$SD_girls_play_male,
  studlab = df$Study,
  data = df,
  comb.fixed = TRUE,
  comb.random = TRUE,
  sm = "SMD"
)
```
# RESUME

📈 First Funnel Plot: Basic Funnel Plot
Axes
X-axis: Standardized Mean Difference (SMD) – representing the effect size (e.g., preference for male-typed toys).

Y-axis: Standard Error – studies with higher precision (larger samples) appear closer to the top.

Interpretation
The graph appears slightly asymmetric, with more studies on the right side of the mean effect line.

This may suggest the presence of publication bias, where studies with significant or positive effects are more likely to be published.

However, a roughly funnel-shaped distribution supports no major bias, although formal tests would be needed to confirm.

📊 Second Funnel Plot: Contour-Enhanced Funnel Plot
Additional Features
This version includes shaded significance contours:

Dark blue: p < 0.01 (very significant)

Blue: p < 0.05 (significant)

Light blue: p < 0.10 (marginally significant)

White: p > 0.10 (non-significant)

Interpretation
Most studies fall in the shaded blue zones, indicating statistically significant results.

The asymmetry, with a lack of points on the left side, may again hint at publication bias.

Studies in the top center region are more precise (smaller standard errors), contributing strongly to the overall result.

The plot confirms the robustness of the meta-analytic finding (SMD ≈ 1), while visually suggesting potential bias due to missing non-significant studies.


```{r}
summary(m_male_toys)
```

```{r}
forest(m_male_toys,
       sortvar = TE,
       xlab = "Standardized Mean Difference (SMD)",
       leftcols = c("studlab", "n.e", "mean.e", "sd.e", "n.c", "mean.c", "sd.c"),
       leftlabs = c("Study", "N boys", "Mean boys", "SD boys", "N girls", "Mean girls", "SD girls"),
       rightcols = c("effect", "ci"),
       rightlabs = c("SMD", "95% CI"),
       col.square = "blue",
       col.diamond = "red",
       col.diamond.lines = "red")
```

```{r}
cat("The standardized mean difference (SMD) of", round(m_male_toys$TE.random, 2), 
    "(", round(m_male_toys$lower.random, 2), "to", round(m_male_toys$upper.random, 2), ") suggests that",
    ifelse(m_male_toys$TE.random > 0, "boys", "girls"),
    "show a", ifelse(abs(m_male_toys$TE.random) > 0.8, "large", 
                    ifelse(abs(m_male_toys$TE.random) > 0.5, "moderate", "small")),
    "preference for male-typed toys compared to", 
    ifelse(m_male_toys$TE.random > 0, "girls", "boys"), ".")
```

```{r}
# Funnel plot simple
funnel(m_male_toys)
```

```{r}
# Contour-enhanced funnel plot
contour_levels <- c(0.90, 0.95, 0.99)
contour_colors <- c("darkblue", "blue", "lightblue")
funnel(m_male_toys, contour = contour_levels, col.contour = contour_colors)
legend("topright", c("p < 0.10", "p < 0.05", "p < 0.01"), bty = "n", fill = contour_colors)
```
